Missing The Point

### 2020-09-11 Manuscript.Rmd
Add convergence diagnostics to outcomes

- Missing data has to be accomodated, usually filled in

@@

- In this paper we explore diagnostic methods for MICE, and show which parameter has the best performance

@@

- outcomes: estimated regression coefficient, CIW, coverage, R2

>>>>

- Missing data has to be accommodated, usually filled in

@@

- In this paper we explore diagnostic methods for MICE, and show which parameter has the best performance --> most informative about convergence

@@

- outcomes: estimated regression coefficient, CIW, coverage, R2 --> multivariate is key, because univariate convergence does not guarantee multivariate convergence
